calibration

### 2017-05-06 Rmd/calibration.Rmd
Various updates towards revision, including new versions of figure 3

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationfffff.xlsx")))
names(cal)

@@

par(mfrow = c(3, 3), mar = c(3, 3, 2, 2), mgp = c(1.5, 0.5, 0))
for(i in varnms) {
  mu <- musmu[, get(i)]
  sdev <- vars[, get(i)]
#   print(paste(i, ":", sdev))
  print(paste(i, ":", round(mu, 2), ":", round(sdev, 2), ":", 
              round(sdev / mu, 2)))
  # plot(mu, sdev / mu, xlab = "mean", ylab = "CV", main = i)
  plot(mu, sdev, xlab = "mean", ylab = "sd", main = i)
}

vars[, lapply(.SD, mean, na.rm = TRUE), .SDcols = varnms]
colMeans(sapply(varnms, function(i) {
  mu <- musmu[, get(i)]
  sdev <- vars[, get(i)]
  sdev / mu
}), na.rm = TRUE)

@@

# calr[feature != 99, ]
# calr[feature != 99, lapply(.SD, mean), by = .(DOI, feature), 
#      .SDcols = rnms[4:7]]
# calr[feature != 99, .N, by = .(DOI, feature)]
calr[feature != 99, lapply(.SD, CV), by = .(DOI, feature), 
     .SDcols = rnms[4:10]][, lapply(.SD, mean, na.rm = TRUE), 
                          .SDcols = rnms[4:10]]

>>>>

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationffffff.xlsx")))
names(cal)

@@

# par(mfrow = c(3, 3), mar = c(3, 3, 2, 2), mgp = c(1.5, 0.5, 0))
# for(i in varnms) {
#   mu <- musmu[, get(i)]
#   sdev <- vars[, get(i)]
# #   print(paste(i, ":", sdev))
#   print(paste(i, ":", round(mu, 2), ":", round(sdev, 2), ":", 
#               round(sdev / mu, 2)))
#   # plot(mu, sdev / mu, xlab = "mean", ylab = "CV", main = i)
#   plot(mu, sdev, xlab = "mean", ylab = "sd", main = i)
# }

vars[, lapply(.SD, mean, na.rm = TRUE), .SDcols = varnms]
round(colMeans(sapply(varnms, function(i) {
  mu <- musmu[, get(i)]
  sdev <- vars[, get(i)]
  sdev / mu
}), na.rm = TRUE), 3)

@@

# calr[feature != 99, ]
# calr[feature != 99, lapply(.SD, mean), by = .(DOI, feature), 
#      .SDcols = rnms[4:7]]
# calr[feature != 99, .N, by = .(DOI, feature)]
mymu <- function(x) round(mean(x, na.rm = TRUE), 3)
calr[feature != 99, lapply(.SD, CV), by = .(DOI, feature), 
     .SDcols = rnms[4:10]][, lapply(.SD, mymu), 
                          .SDcols = rnms[4:10]]
